Fourmile Calibrations and Output

### 2024-06-25 38HRU_model/fourmile_model_outputs.Rmd
params weighted code added

@@

@@

>>>>

# add area weights to params combo
params_weighted <- params_combo %>%
  mutate(area = if_else(burn == 'no', 48243400,
                        18823000)) %>%
  group_by(param, cal) %>%
  summarize(numerator = sum(value * area),
    denominator = sum(area)) %>%
  mutate(area_weighted_average = numerator / denominator) %>%
  dplyr::select(-c(numerator, denominator))

write_csv(params_weighted, './params_weighted.csv')

@@

#
params_weighted1 <- params_weighted %>%
  rename(input_data = cal) %>%
  pivot_wider(names_from = 'param',
              values_from = 'area_weighted_average') %>%
  rename_with(~ paste0(., '_weighted'), 2:7)

@@

join <- left_join(join, params_weighted1, by = 'input_data')
